RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-08 manuscripts/manuscript.Rmd
need to load the library still, silly!
minor formatting

@@

The `RNeXML` package is written entirely in R and available under a
Creative Commons Zero public domain waiver. The current development version can be found
on Github at [https://github.com/ropensci/RNeXML](), and the stable
version can be installed from the CRAN repository.

```{r echo=FALSE, eval=FALSE}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

`RNeXML` is part of the rOpenSci project. Users of `RNeXML` are
encouraged to submit bug reports or feature requests in the issues log
on Github, or to contact `ropensci-discuss@googlegroups.com` or the
phylogenetics R users group list at `r-sig-phylo@r-project.org` for
help.

@@

```{r}
data(bird.orders)
nexml_write(bird.orders, file = "birds.xml")
```

@@

```{r}
library("geiger")
data(geospiza)
nexml_write(trees = geospiza$phy, 
            characters = geospiza$dat,
            file="geospiza.xml")
```

>>>>

```{r echo=FALSE}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

@@

The `RNeXML` package is written entirely in R and available under a
Creative Commons Zero public domain waiver. The current development version can be found
on Github at [https://github.com/ropensci/RNeXML](), and the stable
version can be installed from the CRAN repository.
`RNeXML` is part of the rOpenSci project. Users of `RNeXML` are
encouraged to submit bug reports or feature requests in the issues log
on Github, or the
phylogenetics R users group list at `r-sig-phylo@r-project.org` for
help.

@@

```{r, results='hide'}
data(bird.orders)
nexml_write(bird.orders, file = "birds.xml")
```

@@

```{r, results='hide'}
library("geiger")
data(geospiza)
nexml_write(trees = geospiza$phy, 
            characters = geospiza$dat,
            file="geospiza.xml")
```
